Spin canonical divisors of log stacky curves

### 2015-06-20 stacky_write_up/spin_cring.tex
writing up proof of longer induction

\begin{defn}
\label{defn:admissible}
Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted log stacky curves, ramified over $Q_1,\ldots, Q_r$ and let $J \subset \{1,
\ldots, r\}$. Suppose $e_i'+ 2\chi_J(i) = e_i$ where
$$
\chi_J(i) = \begin{cases}
	1, &\text{ if }i \in J\\
	0, &\text{ otherwise. } 
\end{cases}$$
Let $R'$ be the canonical ring associated to $\sx'$. Say $(\sx',J)$, {\bf admissible} if the following three conditions hold.
\begin{enumerate}
	\item[(Ad-i)] Suppose for all $i \in J$, there exists $y_{i,e_i'} \in R'$ so that $R'$ admits a presentation
\begin{align*}
	R' \cong \left( k[x] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
\end{align*}
so that for all $i \in J$ we have $\deg y_{e_i'} = e_i'$ and $-ord_{Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
\item[(Ad-ii)] For all $i \in J$ and $z \neq y_{i,e_i'}$ a generator of $R'$ we have
\begin{align*}
	\frac{- ord_{Q_i}(z)}{\deg z} < \frac{e_i'-1}{2(e_i')}.
\end{align*}
\item[(Ad-iii)] For all $i \in J$ we have
\begin{align*}
	\deg \lfloor e K_{\sx'} \rfloor \geq \eta(i)
\end{align*}
where
\begin{align*}
	\eta(i) = \#\{j \in J : j \neq i \text{ and }e_j' \mid e_i\}
\end{align*}
\end{enumerate}
\end{defn}

\begin{lem}
\label{lem:admissible_inequality}
Condition 2 of Definition ~\ref{defn:admissible} implies the stronger condition that
\begin{align*}
	-ord(z) \leq \deg(z) \frac{e-3}{2(e-2)}-\frac{1}{e-2}
\end{align*}
\end{lem}

\begin{thm}
\label{thm:ramification_order_induction}
Suppose $(\sx',J)$ is admissible with a generator $y_{e-2} \in R'$ as in condition 1 of Definition ~\ref{defn:admissible}. Then the following are true:
\begin{enumerate}
	\item There exists $y_e \in H^0(\sx, e(K_\sx))$ so that 
	\begin{align*}
	-ord_P(y_e) = \frac{e-1}{2}
\end{align*}
\item The elements $y_{e-2}^ay_e^b,$ with $a \geq 0, b > 0$ span $R$ over $R'$ and the element $y_e$ minimally generates $R$ over $R'$.
\item Equip $k[y]$ and $k[x]$ with any graded monomial order and $k[y,x] = k[y] \otimes k[x]$ with block order. Let $R = k[y,x]/I.$ Then,
\begin{align*}
	in_\prec(I) = in_\prec(I')k[x,y] + \langle y_ez \mid z \neq y_e,y_{e-2} \rangle 
\end{align*}
	as $z$ ranges over generators of $R$.
	\item Suppose $in_\prec(I')$ is minimally generated by quadratics and that $e > \deg z$ for any generator $z$ of $R'.$ Then any set of minimal generators for $I'$ together with any set of relations as in the previous part \todo{reference previous part as part c} minimally generate $I$. \todo{prove this still}
	\item $(\sx,e)$ is admissible.
\end{enumerate}
\end{thm}
\begin{proof}

>>>>

\begin{defn}
\label{defn:admissible}
Let $(\sx',L'),(\sx,L)$ be tame, separably rooted log stacky spin curves, both ramified over ramified at $Q_1,\ldots, Q_r$. Suppose there is a birational map $\sx \rightarrow \sx'$, and let $J \subset \{1,
\ldots, r\}$. Suppose $e_i'+ 2\chi_J(i) = e_i$ where
$$
\chi_J(i) = \begin{cases}
	1, &\text{ if }i \in J\\
	0, &\text{ otherwise. } 
\end{cases}$$
Let $R'$ be the canonical ring associated to $\sx'$. Say $(\sx',J)$, {\bf admissible} if the following three conditions hold.
\begin{enumerate}
	\item[(Ad-i)] Suppose for all $i \in J$, there exists $y_{i,e_i'} \in R'$ so that $R'$ admits a presentation
\begin{align*}
	R' \cong \left( k[x] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
\end{align*}
so that for all $i \in J$ we have $\deg y_{e_i'} = e_i'$ and $-ord_{Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
\item[(Ad-ii)] For all $i \in J$ and $z \neq y_{i,e_i'}$ a generator of $R'$ we have
\begin{align*}
	\frac{- ord_{Q_i}(z)}{\deg z} < \frac{e_i'-1}{2(e_i')}.
\end{align*}
\item[(Ad-iii)] For all $i \in J$ we have
\begin{align*}
	\deg \lfloor e_i L \rfloor \geq \# S(i)
\end{align*}
where
\begin{align*}
	\eta(i) = \{j \in J : j \neq i \text{ and }e_j' \mid e_i\}
\end{align*}
\end{enumerate}
\end{defn}

\begin{lem}
\label{lem:admissible_inequality}
Condition (Ad-ii) of Definition ~\ref{defn:admissible} implies the stronger condition that
\begin{align*}
	-\ord_{Q_i}(z) \leq \deg(z) \frac{e_i'-1}{2e_i'}-\frac{1}{e_i'}
\end{align*}
\end{lem}
\begin{proof}
We know by (Ad-ii) that
\begin{align*}
	-\ord_{Q_i}(z) < \deg(z) \frac{e_i'-1}{2e_i'}
\end{align*}
If we write $\frac{\alpha}{\beta} = \deg(z) \frac{e_i'-1}{2e_i'}$ as a fraction in lowest terms, then we see $\beta \mid e_i'$ since $e_i'-1$ is even. Therefore, since $-\ord_{Q_i}(z)$ is an integer, we must have
\begin{align*}
	-\ord_{Q_i}(z) \leq \deg(z) \frac{e_i'-1}{2e_i'} - \frac{1}{\beta} \leq \deg(z) \frac{e_i'-1}{2e_i'} - \frac{1}{e_i'}.
\end{align*}
\end{proof}

\begin{thm}
\label{thm:ramification_order_induction}
Suppose $(\sx',L')$ is a tame separably rooted log stacky spin curve is admissible with a generators $y_{i,e_i'} \in R' = R_{L'}$ as in (Ad-i) of Definition ~\ref{defn:admissible}. Then the following are true:
\begin{enumerate}
	\item[(a)] For all $i \in J$, there exists $y_{i,e_i} \in H^0(\sx, e_i(K_\sx))$ so that
	\begin{align*}
	-ord_{Q_i}(y_{i,e_i}) = \frac{e_i-1}{2}
\end{align*}
and
\begin{align*}
	\frac{-\ord_{Q_j}(y_{i,e_i'})}{y_{i,e_i}} \leq \frac{e_j'-1}{2e_j'}-\frac{1}{\deg(y_{i,e_i'})e_j'}
\end{align*}
for all $j \in J$ with $j \neq i$.
\item[(b)] The elements $y_{i,e_i'}^ay_{i,e_i}^b,$ with $a \geq 0, b > 0$ span $R$ over $R'$ and the elements $y_{i,e_i}$ minimally generate $R$ over $R'$.
\item[(c)] Equip $k[y] = k[y_{i,e_i}]_{i \in J}$ and $k[x]$ with any graded monomial order and $k[y,x] = k[y] \otimes k[x]$ with block order. Let $R = k[y,x]/I.$ Then,
\begin{align*}
	in_\prec(I) = in_\prec(I')k[x,y] + \langle y_{i,e_i}z \mid z \neq y_{i,e_i},y_{i,e_i'} \rangle 
\end{align*}
	as $z$ ranges over all generators of $R$.
	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by quadratics and that for all $i \in J$, we have $e_i > \deg z$ for any generator $z$ of $R'.$ Then any set of minimal generators for $I'$ together with any set of relations as in the previous part \todo{reference previous part as part c} minimally generate $I$.
	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
\end{enumerate}
\end{thm}
\begin{proof}
Let $(\sx,L)$ and $(\sx',L')$ be the two log stacky spin curves in question. Define
\begin{align*}
	S(i) = \{j \in J : j \neq i \text{ and }e_j' \mid e_i\}
\end{align*}
